Measurement and Probability in Fuzzy Quantum Theories

### 2017-07-15 prop_iop.tex
prop_iop.tex \subsection{Between Expectation Values for Classical and Quantum IVPMs} Updated...

\begin{lemma}\label{lemma:real-expectation-value-between-classical-quantum}Adopting
the definitions in this subsection. Given a density matrix~$\rho$,
there is a classical real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. Then, we have
$\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}

\begin{proof}
\begin{eqnarray*}
\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
 & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\mu'\,.
\end{eqnarray*}
\end{proof}

>>>>

\begin{lemma}\label{lemma:real-expectation-value-between-classical-quantum}Adopting
the definitions in this subsection. Given a density matrix~$\rho$,
there is a classical real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu_{\rho}^{\mathrm{B}}|_{\events'}=\mu'\circ\tau$. Then,
we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}

\begin{proof}Since $\mu_{\rho}^{\mathrm{B}}:\events\rightarrow\left[0,1\right]$
is a QRVPM, $\mu_{\rho}^{\mathrm{B}}|_{\events'}$ is a QRVPM on the
commuting sub-event space\nb$\events'$. By case\nb\ref{enu:sub-event-space-real-quantum2classical}
in theorem~\ref{thm:sub-event-space}, there is a CRVPM such that
$\mu_{\rho}^{\mathrm{B}}|_{\events'}=\mu'\circ\tau$. 
\begin{eqnarray*}
\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
 & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\mu'\,.
\end{eqnarray*}
\end{proof}
